A large-scale study of polymorphism in R

### 2019-03-15 paper/main.tex
minor

\begin{abstract}
The R programming language is widely used in a variety of scientfic domains
for tasks related to data science. The language was designed to favor an
interactive style of programming with minimal syntactic and conceptual
overhead. This design is well suited to support interactive data analysis,
but is not well suited to generating performant code or catching programming
errors.  In particular, R has no type annotations and all operations are
dynamically checked at runtime. The starting point for our work is the
question: \emph{what could a static type system for R look like?}  To answer
that question we study the polymorphism that is present in over X millions
of lines of R code, written over a period of Y years by Z programmers.  We
perform a dynamic analysis, leveraging tests and use-cases, to determine the
level of polymprhism that is present in the code. We do this for several
potential notions of types.
\end{abstract}
\maketitle

>>>>

\begin{abstract}
The R programming language is widely used in a variety of scientfic domains
for tasks related to data science. The language was designed to favor an
interactive style of programming with minimal syntactic and conceptual
overhead. This design is well suited to support interactive data analysis,
but is not well suited to generating performant code or catching programming
errors.  In particular, R has no type annotations and all operations are
dynamically checked at runtime. The starting point for our work is the
question: \emph{what could a static type system for R look like?}  To answer
that question we study the polymorphism that is present in over X millions
of lines of R code, XX packages, written over a period of Y years by Z
programmers.  We perform a dynamic analysis, leveraging tests and use-cases,
to determine the level of polymoprhism that is present in the code. We do
this for several potential notions of types. Our result suggest that
polymorphism is important in some key parts of the system but that
relatively simple type annotations could be used to capture most of the
interesting cases.
\end{abstract}
\maketitle
